Omar Alaa Hasan
Electrical Engineering Student
Riyadh, Saudi Arabia
omar.alaa2004@outlook.sa
+966 56 955 3175
LinkedIn

PROFILE
Electrical Engineering student at KFUPM with hands-on experience in electronics prototyping, embedded development, and engineering software tools. Strong interest in power systems and power engineering, supported by coursework in electric energy engineering and solid fundamentals in circuits and electronics. Comfortable working across hardware and software (C, Python, MATLAB) with practical work on sensors, timing/control, and data-driven analysis. Active in technical leadership and student support through university clubs and the Innovation Hub.

TECHNICAL HIGHLIGHTS
- Electronics & Prototyping: Circuit fundamentals, sensor interfacing concepts, timing/control logic, iterative debugging and testing.
- Power Interest Areas: Electric energy concepts, basic power calculations, and strong motivation to grow in power systems (generation, distribution, protection).
- Software: Python for data analysis and automation; MATLAB for engineering computation; C for embedded programming fundamentals.

EDUCATION
King Fahd University of Petroleum & Minerals (KFUPM), Dhahran
B.S. in Electrical Engineering
Aug 2022 – Expected May 2027
Honors: Third Honor
Selected Coursework: Electronics (EE303), Electric Energy Engineering (EE360), Introduction to Artificial Intelligence (COE292)

EXPERIENCE
iHub — KFUPM Innovation Hub
KFUPM, Dhahran
Jan 2026 – Jun 2026
- Supported workshops and events in electronics, circuits, and technology (equipment preparation, materials, and attendee guidance).
- Helped students troubleshoot technical issues and improve project designs through hands-on support.
- Guided and consulted students on their projects, including design decisions, implementation steps, and structured problem-solving approaches.

PROJECTS

Holographic Fan Display (Persistence of Vision) — EE311
- Designed a low-cost POV display using a high-speed BLDC motor and addressable LEDs with synchronization using a Hall-effect sensor.
- Implemented timing control and a rendering workflow for text/images; validated readability and stability through iterative tuning.
- Practiced system integration: mechanical mounting, wiring, signal timing, and performance testing under realistic indoor conditions.

Factory Expansion Circuit Analysis and Design (Simulation) — EE271 Lab
- Modeled and analyzed a multi-source circuit; computed node voltages, branch currents, and power delivered/absorbed by sources.
- Verified analytical results using circuit simulation, ensuring consistency between hand calculations and simulated behavior.
- Designed an equivalent expansion network connected at terminals (a, b) to meet a target Vab and validated performance.

Air Pollution Classification (Machine Learning) — COE292
- Built a full Python pipeline (cleaning, feature preparation, scaling, train/test split) on a balanced air pollution dataset.
- Trained and evaluated multiple classifiers (e.g., SVM, KNN) using accuracy and confusion-matrix analysis to compare performance.
- Documented findings and recommendations based on model behavior and misclassification patterns.

ADDITIONAL PROJECTS

Embedded Systems Project (EE390 — Part A / Part B) — C / Embedded
- Placeholder: Add what the system did + main peripherals/components used.
- Placeholder: Add your main contribution (implementation, testing, debugging, integration).

Sleep Health & Lifestyle Dataset Analysis — Python
- Placeholder: Add what you explored (EDA, correlations, visualization, baseline models, etc.).

LEADERSHIP AND ACTIVITIES
- Vice President of Media, Electrical Engineering Club (KFUPM).
- Academic Department Leader, Electrical Engineering Club (KFUPM).
- Leader, Electrical Engineering Club Website Team.
- Organizer, ElectraThon Event.
- Member, RoboNexus EEC Team.

SKILLS
- Programming: C (Embedded Fundamentals), Python (Data Analysis/Automation)
- Engineering Tools: MATLAB, KiCad, Fusion 360, Circuit Simulation Tools (e.g., Multisim)
- Hardware: ESP32, Raspberry Pi, basic sensors, prototyping and debugging
- Productivity: Microsoft Office (Excel, PowerPoint, Word)
- Languages: Arabic (Native), English

REFERENCES
Available upon request